Hypercoercions and a Framework for Equivalence of Cast Calculi

### 2019-10-19 paper.tex
use mapsto instead of rightarr, mimic PLT Redex
rename to ADT

\newcommand{\judgeCreduce}[2]{#1 \longrightarrow_{\mathcal{C}} #2}
\newcommand{\judgeCreduceTrans}[2]{#1 \longrightarrow_{\mathcal{C}}^{*} #2}

@@

\newcommand{\redrule}[3]{#1 & \longrightarrow_\mathcal{C} & #2 & #3\\}

@@

\newcommand{\judgeSreduce}[3]{#2 \longrightarrow_{\mathcal{S}(#1)} #3}
\newcommand{\judgeSreduceTrans}[3]{#2 \longrightarrow_{\mathcal{S}(#1)}^{*} #3}

@@

\newcommand{\redruleS}[3]{#1 & \longrightarrow_{\mathcal{S}(C)} & #2 & #3\\}

@@

\newcommand{\judgeDreduce}[2]{#1 \longrightarrow_{\mathcal{D}} #2}
\newcommand{\judgeDreduceTrans}[2]{#1 \longrightarrow_{\mathcal{D}}^{*} #2}

@@

Firstly, let us define what we mean by \emph{cast representations} 
(Definition~\ref{def:cast-rep}). The first three operators allow the 
interpreter to construct casts. We call them \textit{cast constructors}. 
And the forth and last operator enable the interpreter to use casts.

\todo[inline]{Change ``Cast Representation'' to
  ``Cast Abstract Data Type''. -JS}

\begin{definition}[Cast Representation]
	\label{def:cast-rep}
	A cast representation is a set indexed by two types and has four interface 
	functions:
	\begin{description}
		\item[$ id(T) $] constructs an identity cast
		\item[$ seq(c_1,c_2) $] composes two casts
		\item[$ cast(T_1,l,T_2) $] constructs a cast from $ T_1 $ to $ T_2 $
		\item[$ applyCast(v,c) $] applies a cast onto a value
	\end{description}
\end{definition}

\todo[inline]{Change the name ``surely LazyD'' to ``LazyD Cast ADT''. -JS}

To use the framework, users needs to prove that their cast representation is 
\emph{surely LazyD} (Definition~\ref{def:surely-lazyd}).
The definition confines the behavior of $ applyCast(v,c) $ so narrowly that it 
allows the framework to apply casts without referring to the actual definition 
of $ applyCast(v,c) $. This 
is because every casts at runtime is constructed by one of 
the three cast constructors. 
Property (1) handles casts constructed by $ id(T) $. 
And property (2) handles $ seq(c,c) $, which says applying the 
composition of $ c_1 $ and $ c_2 $ is the same as applying $ c_1 $ then $ c_2 $.
All remaining properties handles $ cast(T,l,T) $. They are effectively a 
duplication of the $ applyCast(v,c) $ in \ineffCEKD\ 
(Fig.~\ref{fig:applyCast-D-C}).

\begin{definition}[Surely \lazyD\ Cast Representation]
	\label{def:surely-lazyd}
	A cast representation is surely \lazyD\ if
	\begin{enumerate}
		\item If $ v : T $, then $ applyCast(v,id(T)) = \mathtt{succ} \; v $
		\item If $ \judgeType{v}{T_1} $,
		$ \judgeTypeFT{c_1}{T_1}{T_2} $, and
		$ \judgeTypeFT{c_2}{T_2}{T_3} $,\\
		then $ applyCast(v,seq(c_1,c_2)) = 
		applyCast(v,c_1) >>= \lambda v.applyCast(v,c_2) $ \\
		where 
		\[
		\begin{array}{rcl}
		\rOOsucc{v} >>= f & = & f(v) \\
		\rOOfail{l} >>= f & = & \rOOfail{l}
		\end{array}
		\]
		\item If $ v : T_1 $ and $ \neg T_1 \smile T_2 $,
		then $ applyCast(v,cast(T_1, l, T_2)) = \rOOfail{l} $
		\item If $ v : \star $, 
		then $ applyCast(v,cast(\TOOdyn,l,\TOOdyn)) = \rOOsucc{v} $
		\item If $ v : P_1 $,
		then $ applyCast(\hcvOOinj{P_1}{v},cast(\star,l,P_2)) 
		= applyCast(v,cast(P_1,l,P_2)) $
		\item If $ v : P $,
		then $ applyCast(v,cast(P,l,\star)) = \rOOsucc{(\hcvOOinj{P}{v})} $
		\item If $ v : \POOunit $,
		then $ applyCast(v,cast(\POOunit,l,\POOunit)) = \rOOsucc{v} $
		\item
		$ 
		applyCast(\hcvOOfun{c_1}{\rho}{x}{b}{c_2}, 
		cast(\POOfun{T_1}{T_2},l,\POOfun{T_3}{T_4})) \\
		= 
		\rOOsucc{(\hcvOOfun{seq(cast(T_3,l,T_1),c_1)}{\rho}{x}{b}{seq(c_2,cast(T_2,l,T_4))})}$

@@

If a cast representation is surely LazyD, proving this should be easier than 
proving equivalence to the standard semantics of cast calculus.

@@

\begin{definition}[Monoid]
	A cast representation is a monoid if 
	for all
	$c_1 : T_1 \Longrightarrow T_2$,
	$c_2 : T_2 \Longrightarrow T_3$, and
	$c_3 : T_3 \Longrightarrow T_4$,
	\begin{enumerate}
		\item $seq(id(T_1),c_1) = c_1$,
		\item $seq(c_1,id(T_2)) = c_1$, and
		\item $seq(seq(c_1, c_2), c_3) = seq(c_1, seq(c_2, c_3))$.
	\end{enumerate}
\end{definition}

In subsection~\ref{ssec:framework:cek}, we introduce \effCEK{C}, a family 
of space-efficient semantics indexed by cast representations ($ C $). 
In subsection~\ref{secc:framework:monoid-correct}, we prove when $ C $ is 
$ surely \; \text{\lazyD} $ and is a monoid as well, $ \judgeDeval{e}{o} $ if 
and only if $ \judgeSeval{C}{e}{o} $. In 
subsection~\ref{secc:framework:all-correct}, we strengthen the theorem to drop 
the requirement that $ C $ must be a monoid, that is, every surely \lazyD\ cast 
representation is correct.

@@

\subsection{Surely \lazyD\ Cast Representations Respect \ineffCEKD\ if They are 
Monoids}
\label{secc:framework:monoid-correct}

In this subsection, we prove that for all $ C $, if $ C $ is surely LazyD and 
is a monoid, then $ \judgeDeval{e}{o} $ if and only if $ \judgeSeval{C}{e}{o} 
$. We proof this theorem with a weak bisimulation between \ineffCEKD\ and 
\effCEK{C}.

@@

\begin{lemma}[Weak Bisimulation between \effCEK{C} and \ineffCEKD]
	\label{thm:surely-monoidic-reduce}
	For all cast representations $ C $, 
	if $ C $ is surely \lazyD{} and is a monoid, 
	$ s_{1}, s_{1}' \in \text{\effCEK{C}} $,
	$ s_{2}, s_{2}' \in \text{\ineffCEKD} $,
	$ s_{1} \approx s_{2} $,
	$ \judgeSreduce{C}{s_{1}}{s_{1}'} $, and
	$ \judgeDreduce{s_{2}}{s_{2}'} $, then
%	then there exist $ s_2'' \in \text{\ineffCEKD} $ such that
	\[ \exists s_2'' \in \text{\ineffCEKD}: \;
	\judgeDreduceTrans{s_{2}'}{s_{2}''} \;\text{and}\; s_1' \approx s_2'' \]
%	\begin{enumerate}
%		\item If $ \judgeDreduce{s_1}{s_3} $,
%		then
%		there exist $ s_5 \in \text{\ineffCEKD} $, $ s_4 \in \mathcal{S}(C) $,
%		such that \begin{itemize}
%			\item $ s_5 \approx s_4 $, and
%			\item $ \judgeSreduce{C}{s_2}{s_4} $,
%			\item $ \judgeDreduceTrans{s_3}{s_5} $
%		\end{itemize}
%		\item If $ \judgeSreduce{C}{s_2}{s_4} $,
%		then
%		there exist $ s_3 \in \mathcal{C} $,
%		such that \begin{itemize}
%			\item $ s_3 \approx s_4 $
%			\item $ \judgeDreduceTrans{s_1}{s_3} $
%		\end{itemize}
%	\end{enumerate}

@@

\begin{lemma}[Surely \lazyD\ and Monoidic Cast Representations Respect 
	$ \mathcal{C} $]
	\label{thm:surely-monoidic-eval}
	If $ \judgetype{\emptyset}{e}{T} $ and $ o : T $ and $ C $ is surely 
	\lazyD{} and is a monoid,
	\[
	\judgeSeval{C}{e}{o}
	 \; \text{if and only if} \; 
	\judgeDeval{e}{o}
	\]
\end{lemma}
\begin{proof}Proving left implies right is trivial.
To prove $ \judgeDeval{e}{o} $ implies $ \judgeSeval{C}{e}{o} $, 
we firstly take one steps in \effCEK{C}, and catch it up in \ineffCEKD\ by 
taking one or more steps in \ineffCEKD. As we just took a positive number of 
steps, we are closer to the halting state.
\end{proof}

\subsection{Surely \lazyD\ Cast Representations Respect \ineffCEKD}
\label{secc:framework:all-correct}

In this subsection, we prove that for all $ C $, if $ C $ is surely LazyD, then 
$ \judgeDeval{e}{o} $ if and only if $\judgeSeval{C}{e}{o}$. We first prove 
that all $ S(C) $ where $ C $ is surely lazyD are equivalent, then connect this 
theorem to Lemma~\ref{thm:surely-monoidic-eval}.

@@

\begin{lemma}[Strong Bi-simulation among $ \mathcal{S}(\cdot) $]
	\label{thm:CEKS-bisim}
	If 
	$ C_1 $ and $ C_2 $ are surely \lazyD,
	$ s_1, s_1' \in S(C_1) $ and $ s_2,s_2' \in S(C_2) $,
	$ s_1 \approx s_2 $,
	$ \judgeSreduce{C_1}{s_1}{s_1'} $, and
	$ \judgeSreduce{C_2}{s_2}{s_2'} $, then 
	$ s_1' \approx s_2' $

	Or diagrammatically, 
	\[\begin{array}{clc}
	s_{1} & \longrightarrow_{\text{\effCEK{C}}} & s_1'\\
	\rotatebox[origin=c]{90}{$\approx$} 
	& & \rotatebox[origin=c]{90}{$\approx$} \\
	s_{2} & 
	\longrightarrow_{\text{\ineffCEKD}} & s_2' \\
	\end{array}\]
\end{lemma}
\begin{proof} 
	This proof is effectively a duplication of the transition rule of 
	\effCEK{S(C)}.
	The key ideas of this proof are undoing sequencing with the property (2) of 
	surely \lazyD{} cast representation, and handling all possibly uses of $ 
	cast(T,l,T) $ with property (3)-(11).
\end{proof}

\begin{proposition}[Equivalence of Surely \lazyD{} Cast Representations]
	\label{thm:surely-lazyD-eqv}
	If $ \judgetype{\emptyset}{e}{T} $, $ o : T $, and $ C_1 $ and $ C_2 $ 
	are surely \lazyD\ cast representations,
	\[
	e \Downarrow_{S(C_1)} o \; \text{if and only if} \; 
	e \Downarrow_{S(C_2)} o
	\]
\end{proposition}
\begin{proof}
	By induction with the help of Lemma~\ref{thm:CEKS-bisim}.
\end{proof}

\begin{theorem}[Surely \lazyD\ Cast Representations Respect \ineffCEKD]
	\label{thm:surely-lazyD-correct}
	If $ \judgetype{\emptyset}{e}{T} $ and $ o : T $ and $ C $ is surely 
	\lazyD{}
	\[
	\judgeCeval{e}{o} \; \text{if and only if} \; 
	\judgeSeval{C}{e}{o}
	\]
\end{theorem}
\begin{proof}
	If we have a surely LazyD cast representation and it is a monoid, this 
	proof is immediately from Lemma~\ref{thm:surely-monoidic-eval} and 
	Proposition~\ref{thm:surely-lazyD-eqv}. One such representation is to 
	represent casts as a list of triples of type, label, and type, where $ 
	id(T) $ is the empty list and $ seq(c,c,) $ is list append. Another such 
	representation is the \lazyD\ hypercoercion!
\end{proof}

@@

In this section we prove \lazyD\ hypercoercion, as a cast representation, is 
correct. First we define $ applyCast(v,c) $ to make it a cast representation, 
then prove that it is surely lazyD, and finally apply 
Theorem~\ref{thm:surely-lazyD-correct} to finish the proof.

%To use hypercoercion as a 
%cast representation in our framework, we need to defined four functions: $ 
%cast(T,l,T) $, $ id(T) $, $ seq(c,c) $, and . We have defined 
%the first three functions in Section~\ref{sec:hypercoercion-definition}. Now 
%we 
%define the $ applyCast(v,c) $  in

@@

\begin{lemma}[\lazyD{} hypercoercion is Surely \lazyD]
	\label{thm:hc-surely-lazyD}
\end{lemma}
\begin{proof} See the supplementary material. \end{proof}

>>>>

\newcommand{\judgeCreduce}[2]{#1 \longmapsto_{\mathcal{C}} #2}
\newcommand{\judgeCreduceTrans}[2]{#1 \longmapsto_{\mathcal{C}}^{*} #2}

@@

\newcommand{\redrule}[3]{#1 & \longmapsto_\mathcal{C} & #2 & #3\\}

@@

\newcommand{\judgeSreduce}[3]{#2 \longmapsto_{\mathcal{S}(#1)} #3}
\newcommand{\judgeSreduceTrans}[3]{#2 \longmapsto_{\mathcal{S}(#1)}^{*} #3}

@@

\newcommand{\redruleS}[3]{#1 & \longmapsto_{\mathcal{S}(C)} & #2 & #3\\}

@@

\newcommand{\judgeDreduce}[2]{#1 \longmapsto_{\mathcal{D}} #2}
\newcommand{\judgeDreduceTrans}[2]{#1 \longmapsto_{\mathcal{D}}^{*} #2}

@@

We captures the set of operators that every cast representation must provide 
with \emph{cast abstract data type} (Definition~\ref{def:cast-rep}). 
The first three operators allow a language implementation to construct casts. 
So we call them \textit{cast constructors}. And the forth and last operator 
enable the implementation to use apply casts.

\todo[inline]{Change ``Cast Representation'' to
  ``Cast Abstract Data Type''. -JS
\\---\\
Fixed -KC}

\begin{definition}[Cast Abstract Data Type (Cast ADT)]
	\label{def:cast-rep}
	A cast abstract data type is a set $ Cast $ indexed by two types with
	four operators:
	\begin{description}
		\item[$ id(T) = c $] constructs an identity cast
		\item[$ seq(c_1,c_2)=c $] composes two casts
		\item[$ cast(T_1,l,T_2)=c $] constructs a cast from $ T_1 $ to $ T_2 $
		\item[$ applyCast(v,c)=r $] applies a cast onto a value
	\end{description}
\end{definition}

\todo[inline]{Change the name ``surely LazyD'' to ``LazyD Cast ADT''. -JS
\\---\\
Fixed -KC}

To use our framework, users needs to prove that their cast representation 
implements Lazy D Cast ADT (Definition~\ref{def:surely-lazyd}).
The definition confines the behavior of $ applyCast(v,c) $ so narrowly that it 
allows the framework to apply casts without referring to the actual definition 
of $ applyCast(v,c) $. This 
is because every casts at runtime is constructed by one of 
the three cast constructors. 
Property (1) handles casts constructed by $ id(T) $. 
And property (2) handles $ seq(c,c) $, which says applying the 
composition of $ c_1 $ and $ c_2 $ is the same as applying $ c_1 $ then $ c_2 $.
All remaining properties handles $ cast(T,l,T) $. They are effectively a 
duplication of the $ applyCast(v,c) $ in \ineffCEKD\ 
(Fig.~\ref{fig:applyCast-D-C}).

\begin{definition}[Lazy D Cast ADT]
	\label{def:surely-lazyd}
	A  Cast ADT is a Lazy D Cast ADT if:
	\begin{enumerate}
		\item If $ v : T $, then $ applyCast(v,id(T)) = \mathtt{succ} \; v $
		\item If $ \judgeType{v}{T_1} $,
		$ \judgeTypeFT{c_1}{T_1}{T_2} $, and
		$ \judgeTypeFT{c_2}{T_2}{T_3} $,\\
		then $ applyCast(v,seq(c_1,c_2)) = 
		applyCast(v,c_1) >>= \lambda v.applyCast(v,c_2) $ \\
		where 
		\[
		\begin{array}{rcl}
		\rOOsucc{v} >>= f & = & f(v) \\
		\rOOfail{l} >>= f & = & \rOOfail{l}
		\end{array}
		\]
		\item If $ v : T_1 $ and $ \neg T_1 \smile T_2 $,
		then $ applyCast(v,cast(T_1, l, T_2)) = \rOOfail{l} $
		\item If $ v : \star $, 
		then $ applyCast(v,cast(\TOOdyn,l,\TOOdyn)) = \rOOsucc{v} $
		\item If $ v : P_1 $,
		then $ applyCast(\hcvOOinj{P_1}{v},cast(\star,l,P_2)) 
		= applyCast(v,cast(P_1,l,P_2)) $
		\item If $ v : P $,
		then $ applyCast(v,cast(P,l,\star)) = \rOOsucc{(\hcvOOinj{P}{v})} $
		\item If $ v : \POOunit $,
		then $ applyCast(v,cast(\POOunit,l,\POOunit)) = \rOOsucc{v} $
		\item
		$ 
		applyCast(\hcvOOfun{c_1}{\rho}{x}{b}{c_2}, 
		cast(\POOfun{T_1}{T_2},l,\POOfun{T_3}{T_4})) \\
		= 
		\rOOsucc{(\hcvOOfun{seq(cast(T_3,l,T_1),c_1)}{\rho}{x}{b}{seq(c_2,cast(T_2,l,T_4))})}$

@@

If a cast representation is a Lazy D Cast ADT, people can apply our theorems 
and be confident that this cast representation is valid.

@@

\begin{definition}[Monoid]
	A Cast ADT is a monoid if 
	for all
	$c_1 : T_1 \Longrightarrow T_2$,
	$c_2 : T_2 \Longrightarrow T_3$, and
	$c_3 : T_3 \Longrightarrow T_4$,
	\begin{enumerate}
		\item $seq(id(T_1),c_1) = c_1$,
		\item $seq(c_1,id(T_2)) = c_1$, and
		\item $seq(seq(c_1, c_2), c_3) = seq(c_1, seq(c_2, c_3))$.
	\end{enumerate}
\end{definition}

In subsection~\ref{ssec:framework:cek}, we introduce \effCEK{C}, a family 
of space-efficient semantics indexed by Cast ADTs ($ C $). 
In subsection~\ref{secc:framework:monoid-correct}, we prove when $ C $ is
a Lazy D Cast ADT and a monoid as well, $ \judgeDeval{e}{o} $ if 
and only if $ \judgeSeval{C}{e}{o} $. In 
subsection~\ref{secc:framework:all-correct}, we strengthen the theorem to drop 
the requirement that $ C $ must be a monoid, that is, every instance of Lazy D 
Cast ADT is correct.

@@

\subsection{\lazyD\ Cast ADTs Respect \ineffCEKD\ if They are 
Monoids}
\label{secc:framework:monoid-correct}

In this subsection, we prove that if a instance of Cast ADT $ C $ is Lazy D and 
is a monoid, then $ \judgeDeval{e}{o} $ if and only if $ \judgeSeval{C}{e}{o} 
$. We proof this theorem with a weak bisimulation between \ineffCEKD\ and 
\effCEK{C}.

@@

\begin{lemma}[Weak Bisimulation between \effCEK{C} and \ineffCEKD]
	\label{thm:surely-monoidic-reduce}
	For all instance of Cast ADT $ C $, 
	if $ C $ is \lazyD{} and is a monoid, 
	$ s_{1}, s_{1}' \in \text{\effCEK{C}} $,
	$ s_{2}, s_{2}' \in \text{\ineffCEKD} $,
	$ s_{1} \approx s_{2} $,
	$ \judgeSreduce{C}{s_{1}}{s_{1}'} $, and
	$ \judgeDreduce{s_{2}}{s_{2}'} $, then
%	then there exist $ s_2'' \in \text{\ineffCEKD} $ such that
	\[ \exists s_2'' \in \text{\ineffCEKD}: \;
	\judgeDreduceTrans{s_{2}'}{s_{2}''} \;\text{and}\; s_1' \approx s_2'' \]
%	\begin{enumerate}
%		\item If $ \judgeDreduce{s_1}{s_3} $,
%		then
%		there exist $ s_5 \in \text{\ineffCEKD} $, $ s_4 \in \mathcal{S}(C) $,
%		such that \begin{itemize}
%			\item $ s_5 \approx s_4 $, and
%			\item $ \judgeSreduce{C}{s_2}{s_4} $,
%			\item $ \judgeDreduceTrans{s_3}{s_5} $
%		\end{itemize}
%		\item If $ \judgeSreduce{C}{s_2}{s_4} $,
%		then
%		there exist $ s_3 \in \mathcal{C} $,
%		such that \begin{itemize}
%			\item $ s_3 \approx s_4 $
%			\item $ \judgeDreduceTrans{s_1}{s_3} $
%		\end{itemize}
%	\end{enumerate}

@@

\begin{lemma}[$ \text{Lazy D Cast ADT} \cap \text{Monoid} $ Respects 
	$ \mathcal{C} $]
	\label{thm:surely-monoidic-eval}
	If $ \judgetype{\emptyset}{e}{T} $ and $ o : T $ and $ C $ is a 
	\lazyD{} Cast ADT and a monoid,
	\[
	\judgeSeval{C}{e}{o}
	 \; \text{if and only if} \; 
	\judgeDeval{e}{o}
	\]
\end{lemma}
\begin{proof}Proving left implies right is trivial.
To prove $ \judgeDeval{e}{o} $ implies $ \judgeSeval{C}{e}{o} $, 
we firstly take one steps in \effCEK{C}, and catch it up in \ineffCEKD\ by 
taking one or more steps in \ineffCEKD. As we just took a positive number of 
steps, we are closer to the halting state.
\end{proof}

\subsection{\lazyD\ Cast ADT Respect \ineffCEKD}
\label{secc:framework:all-correct}

In this subsection, we prove that for all $ C $, if $ C $ is a Lazy D Cast ADT, 
then $ \judgeDeval{e}{o} $ if and only if $\judgeSeval{C}{e}{o}$. We first 
prove that all $ S(C) $ where $ C $ is a Lazy D Cast ADT are equivalent, then 
connect this theorem to Lemma~\ref{thm:surely-monoidic-eval}.

@@

\begin{lemma}[Strong Bi-simulation among $ \mathcal{S}(\cdot) $]
	\label{thm:CEKS-bisim}
	If 
	$ C_1 $ and $ C_2 $ are instances of Lazy D Cast ADT,
	$ s_1, s_1' \in S(C_1) $ and $ s_2,s_2' \in S(C_2) $,
	$ s_1 \approx s_2 $,
	$ \judgeSreduce{C_1}{s_1}{s_1'} $, and
	$ \judgeSreduce{C_2}{s_2}{s_2'} $, then 
	$ s_1' \approx s_2' $

	Or diagrammatically, 
	\[\begin{array}{clc}
	s_{1} & \longrightarrow_{\text{\effCEK{C}}} & s_1'\\
	\rotatebox[origin=c]{90}{$\approx$} 
	& & \rotatebox[origin=c]{90}{$\approx$} \\
	s_{2} & 
	\longrightarrow_{\text{\ineffCEKD}} & s_2' \\
	\end{array}\]
\end{lemma}
\begin{proof} 
	This proof is effectively a duplication of the transition rule of 
	\effCEK{S(C)}.
	The key ideas of this proof are undoing sequencing with the property (2) of 
	Lazy D Cast ADT, and handling all possibly uses of $ 
	cast(T,l,T) $ with property (3)-(11).
\end{proof}

\begin{proposition}[Equivalence of \lazyD{} Cast ADT]
	\label{thm:surely-lazyD-eqv}
	If $ \judgetype{\emptyset}{e}{T} $, $ o : T $, and $ C_1 $ and $ C_2 $ 
	are \lazyD\ Cast ADTs,
	\[
	e \Downarrow_{S(C_1)} o \; \text{if and only if} \; 
	e \Downarrow_{S(C_2)} o
	\]
\end{proposition}
\begin{proof}
	By induction with the help of Lemma~\ref{thm:CEKS-bisim}.
\end{proof}

\begin{theorem}[\lazyD\ Cast ADT Respects \ineffCEKD]
	\label{thm:surely-lazyD-correct}
	If $ \judgetype{\emptyset}{e}{T} $ and $ o : T $ and $ C $ is a 
	\lazyD{} Cast ADT.
	\[
	\judgeCeval{e}{o} \; \text{if and only if} \; 
	\judgeSeval{C}{e}{o}
	\]
\end{theorem}
\begin{proof}
	If we have a surely LazyD Cast ADT and it is a monoid, this 
	proof is immediately from Lemma~\ref{thm:surely-monoidic-eval} and 
	Proposition~\ref{thm:surely-lazyD-eqv}. One such representation is to 
	represent casts as a list of triples of type, label, and type, where $ 
	id(T) $ is the empty list and $ seq(c,c,) $ is list append. Another such 
	representation is the \lazyD\ hypercoercion!
\end{proof}

@@

In this section we prove \lazyD\ hypercoercion is 
correct. First we define $ applyCast(v,c) $ to make it an instance of Cast ADT, 
then prove that it is also Lazy D, and finally apply 
Theorem~\ref{thm:surely-lazyD-correct} to finish the proof.

@@

\begin{lemma}[\lazyD{} hypercoercion is a \lazyD Cast ADT]
	\label{thm:hc-surely-lazyD}
\end{lemma}
\begin{proof} See the supplementary material. \end{proof}
